Coherent optical association of a single molecule

### 2020-11-04 paper.tex
Mention power/b field stability requirements

\todo{change scattering to decoherence? since the fluctuation of light shift
  does not lead to scattering but only decherence.}
These results suggest that the decoherence or loss we observed during the Raman transition
comes from either a higher than expected background scattering rate
or a different intrinsic or technical source that we have not accounted for.
We have observed a significant decrease in the coherence time without the ASE filter,
suggesting the spectral purity of the laser is a significant source of scattering.
Another source of decoherence could result from fluctuations in the power ratio
between the two beams resulting in a fluctuation in the resonance position.
In the experiment, we only stabilize the total power of the tweezer.

In additional to calibrating the $\Omega_m$ and $\Omega_a$,
the scattering rate of the molecule depends on the tweezer power and detuning.
At $3\mathrm{mW}$ tweezer power, we have observed a molecule lifetime as long as $1~\mathrm{ms}$.
However, since the technical noise that can lead to decoherence
is not fully characterized in our experiment,
we are unable to further identify the sources of the measured scattering rate based on our measured detuning and power dependencies.
% the discrepancy based on the dependency.

@@

%%%% Maybe this following section about the B field can be relegated to a figure caption?
% Figure () shows the geometry of the experiment setup. A $8.8\mathrm{G}$ B field was used to defines the quantization axis in the experiment and is applied perpendicular to the tweezer axis. The tweezer beam (both frequencies for the Raman transition) has a $\pi$ polarization relative to the quantization axis, which allows us to selectively drive the Raman transition to a final state with the same total $m_F$ quantum number as our initial state.
\todo{}B field dependency $42.2(2) \mathrm{kHz/G}$.

>>>>

\todo{change scattering to decoherence? since the fluctuation of light shift
  does not lead to scattering but only decherence.}
These results suggest that the decoherence or loss we observed during the Raman transition
comes from either a higher than expected background scattering rate
or a different intrinsic or technical source that we have not accounted for.
We have observed a significant decrease in the coherence time without the ASE filter,
suggesting the spectral purity of the laser is a significant source of scattering.
Other sources that can contribute to the decoherence includes
the stability of the tweezer power and the magnetic field.
Based on the Raman Rabi frequency to light shift ratio (Fig.~\ref{f-det}c),
the requirement on the tweezer power stability is $0.8~\%$ at $15~\mathrm{mW}$.
We stabilize the tweezer power to $0.1~\%$ so this should not be a major source
of decoherence.
Similarly, we measured a Zeeman shift of $42.2(2)~\mathrm{kHz/G}$
which does not cause significant decoherence from the measured magnetic field
fluctuation of $\sim1.5~\mathrm{mG}$.

In additional to calibrating the $\Omega_m$ and $\Omega_a$,
the scattering rate of the molecule depends on the tweezer power and detuning.
At $3\mathrm{mW}$ tweezer power, we have observed a molecule lifetime as long as $1~\mathrm{ms}$.
However, since the technical noise that can lead to decoherence
is not fully characterized in our experiment,
we are unable to further identify the sources of the measured scattering rate
based on our measured detuning and power dependencies.

@@
